figures and calculations for global fisheries management

### 2019-01-14 documents/figs-and-calcs.Rmd
added in example economic figures, started standardizing figure formats

```{r load}
library(tidyverse)
library(readxl)
library(tidyxl)
library(here)

@@

@@

projection_data_fig1$Dbase[projection_data_fig1$Dbase == "RAM"]<- "Stock Assessed"
projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Stock Not Assessed"

assessed <- projection_data_fig1%>% filter(Dbase == "Stock Assessed")
notassessed <- projection_data_fig1 %>% filter(Dbase == "Stock Not Assessed")

fig_1 = projection_data_fig1 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 1")+
  geom_point(data= assessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
  geom_point(data= notassessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)

@@

#ggsave(here("documents/figures","figure-1.pdf"), fig_1)

@@

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, aes(fill = CatchShare)) +
  ggtitle("Figure 2")

fig_2

#ggsave(here("documents/figures","figure-2.pdf"), fig_2)

@@

fig_3 = projection_data_fig3 %>%
  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
  scale_alpha(range = c(0.5, 1))+
  theme_minimal() +
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
  ggtitle("Figure 3") +
  geom_point(data= rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
  geom_point(data= no_rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)

@@

#ggsave(here("documents/figures","figure-3.pdf"), fig_3)
```

@@

@@

@@

unique(turf_catch_upper$assess_id_short)
#27 fisheries with turfs

itqs <-projection_corb%>%
  filter(itq == "TRUE" | ivq == "TRUE" | iq == "TRUE")
unique(itqs$assess_id_short)
#94

turf_all_1 <- full_join(edf_turf, d_turfs, by= c("Country", "SciName"))
projection_turf <- projection_corb %>%
  filter(turf == "TRUE") %>%
  select("Country", "SciName")

@@

everything_fit <-
  multinom(
    formula = CatchShare ~ gdp_center + SpeciesCatName,
    family = "binomial",
    data = upjoin
  )

>>>>

```{r load}
library(tidyverse)
library(readxl)
library(tidyxl)
library(here)
library(hrbrthemes)
library(extrafont)

extrafont::loadfonts()

@@

fig_width <- 8

fig_height <- 6

theme_set(theme_ipsum(base_size = 14))

@@

projection_data_fig1$Dbase[projection_data_fig1$Dbase == "RAM"]<- "Stock Assessed"
projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Unassessed"

assessed <- projection_data_fig1%>% filter(Dbase == "Stock Assessed")
notassessed <- projection_data_fig1 %>% filter(Dbase == "Unassessed")

medians <- assessed %>% 
  bind_rows(notassessed) %>% 
  group_by(Dbase) %>% 
  summarise(median_b = median(BvBmsy),
            median_f = median(FvFmsy))

fig_1 = projection_data_fig1 %>%
  ggplot() + 
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  geom_point(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
  coord_cartesian(xlim = c(0,2.5), ylim = c(0,4))+
  theme_minimal() +
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
    geom_point(data= medians, aes(x=median_b,y=median_f, fill = Dbase),shape = 24, size = 10, alpha = 0.75)  + 
  scale_color_discrete(name = '') + 
    scale_fill_discrete(name = '') + 
  scale_size_continuous(labels = scales::comma) + 
  scale_alpha_continuous(labels = scales::comma, range = c(0.25,1))

@@

ggsave(here("figures","figure-1.pdf"), fig_1, width = fig_width, height = fig_height)

@@

fig_2 = ggplot() +
  geom_sf(data= projection_spatial, aes(fill = CatchShare == 1), size = 0.1) +
  scale_fill_discrete(name = "Has Catch Shares?") + 
  ggthemes::theme_map()

# fig_2

ggsave(here("figures","figure-2.pdf"), fig_2, height = fig_height, width = fig_width)

@@

medians <- rbfm %>% 
  bind_rows(no_rbfm) %>% 
  group_by(CatchShare) %>% 
  summarise(median_b = median(BvBmsy),
            median_f = median(FvFmsy))

fig_3 = projection_data_fig3 %>%
  # mutate(CatchShare = ifelse(CatchShare == 1, "RBFM","No RBFM")) %>% 
  ggplot() + 
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  geom_point(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
  coord_cartesian(xlim = c(0,2.5), ylim = c(0,4))+
  theme_minimal() +
  xlab("B/Bmsy")+
  ylab("F/Fmsy") +
    geom_point(data= medians, aes(x=median_b,y=median_f, fill = CatchShare),shape = 24, size = 10, alpha = 0.75)  + 
  scale_color_discrete(name = '') + 
    scale_fill_discrete(name = '') + 
  scale_size_continuous(labels = scales::comma) + 
  scale_alpha_continuous(labels = scales::comma, range = c(0.25,1))

@@

ggsave(here("figures","figure-3.pdf"), fig_3, height = fig_height, width = fig_width)

@@

```{r fig-4}
r <- 0.2

k <- 100

p <- 2

msy <- r*k/4

b_oa <- 0.25

f_oa <- 2 - b_oa

cost <- (p*msy * f_oa * b_oa) / (f_oa * r/2)^2

demo <- tibble(biomass = seq(0,k, by = .1)) %>% 
  mutate(b = biomass / (k / 2),
         f = 2 - b,
         Costs = cost * (f * r/2)^2,
         Profits = p * msy * f * b - Costs,
         Revenue =  p * msy * f * b,
         catch = msy * f * b)

b_mey <- demo$biomass[demo$Profits == max(demo$Profits)][1]

demo <- demo %>% 
  gather(metric,value, -biomass)

figure_4 <- demo %>% 
  filter(tolower(metric) %in% c("profits", "costs", "revenue")) %>% 
  ggplot() + 
  geom_line(aes(biomass,value, color = metric), size = 2) + 
  ggsci::scale_color_simpsons(name = "") + 
  theme_classic() + 
  labs(y = "Value", x = "Fish Biomass") + 
  geom_vline(aes(xintercept = b_oa * k / 2), color = "red", linetype = 2) + 
  geom_vline(aes(xintercept = b_mey), color = "blue", linetype = 2) + 
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = expand_scale(mult = 0, add = c(0, .2)), limits = c(0,NA),
                     breaks = c(0,max(demo$value)), labels = c("Low","High"))

figure_4
ggsave(here("figures","figure-4.pdf"), figure_4, height = fig_height, width = fig_width)
```

@@

repeat analysis but with a grid of F/Fmsy by discount rate and cost parameter

find fopt for any given scenario
```{r fig-6, cache = TRUE}

scenes <- purrr::cross_df(list(cost = seq(100,1500, by = 50), 
                               discount = seq(0,0.5, by = 0.01)))

popfoo <- function(f,cost, discount,r,k,p,d0 = 1,beta, time = 100, use = 0){

  out <-
    tibble(
      b = rep(NA, time)
    )

  out$b[1] <- k * d0

  for (t in 2:(time)) {
    out$b[t] <-
      out$b[t - 1] + out$b[t - 1] * r * (1 - out$b[t - 1] / k) - f * out$b[t - 1]

  }

  out <- out %>% 
    mutate(f_rate = f,
           catches = b * f_rate,
           revenue = p * catches,
           costs = cost*f_rate^2,
           profits = revenue - costs,
           year = seq_along(b))

  npv <- sum(out$profits * (1 + discount)^-(0:(time - 1)))

if (use == 0){
  out <- -npv
} else {
  out <- out
}

}

test <- nlminb(.05, popfoo, cost = 0, discount = 0, r = 0.2, k = 100, p = 2, beta = 2, lower = 0, upper = 0.99, time = 1000)

check <- popfoo(f = test$par,cost = 0, discount = 0, r = 0.2, k = 100, p = 2, beta = 2,use = 2, time = 1000)

fmeyfoo <- function(cost,discount,r = 0.2,k = 100,p = 2,beta = 2, time = 1000){

  out <- nlminb(r/2,popfoo,cost = cost, discount = discount, r = r, k = k, p = p, beta = beta,use = 0, time = time)

  out <- out$par

}

r <- 0.2

k <- 100

p <- 2

beta <- 2

time <- 200

results <- scenes %>%
  mutate(fmey = map2_dbl(
    cost,
    discount,
    fmeyfoo,
    r = r,
    k = k,
    p = p,
    beta = beta,
    time = time
  )) %>%
  mutate(mey_pop = pmap(
    list(
      f = fmey,
      cost = cost,
      discount = discount
    ),
    popfoo,
      r = r,
      k = k,
      p = p,
      beta = beta,
      use = 2,
      time = time
    )
  )

results <- results %>% 
  unnest()

figure_6 <- results %>%
  filter(year == max(year)) %>%
  ggplot() +
  geom_raster(aes(cost, discount, fill = b / (k/2)),
              interpolate = TRUE) +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = c(min(scenes$cost), 750, 1500),
    labels = c("Low", "Medium", "High"),
    name = "Fishing Costs"
  ) +
  scale_y_continuous(expand = c(0, 0),
                     name = "Discount Rate",
                     labels = scales::percent) +
  scale_fill_gradient2(
    low = "tomato",
    mid = "white",
    high = "steelblue",
    midpoint = 1,
    name = "Bmey",
    guide = guide_colorbar(frame.colour = "black",
                           barheight = unit(15, "lines")),
    limits = c(0,2)
  ) + 
  theme(panel.border = element_rect(color = "black",
                                    fill = "transparent"))

figure_6

ggsave(here("figures","figure-6.pdf"), figure_6, height = fig_height, width = fig_width)
```

@@

projection_data <- readRDS(here("data","projection_data.rds")) %>% 
  filter(Scenario == "Historic")
unique(turf_catch_upper$assess_id_short)
#27 fisheries with turfs

itqs <-projection_corb%>%
  filter(itq == "TRUE" | ivq == "TRUE" | iq == "TRUE")
# unique(itqs$assess_id_short)
#94

turf_all_1 <- full_join(edf_turf, d_turfs, by= c("Country", "SciName"))

projection_turf <- projection_corb %>%
  filter(turf == "TRUE") %>%
  select("Country", "SciName")

@@

everything_fit <-
  nnet::multinom(
    formula = CatchShare ~ gdp_center + SpeciesCatName,
    family = "binomial",
    data = upjoin
  )
